Data Exploration: IUCN and AquaMaps

### 2016-08-02 coralmaps/coral_maps.Rmd
ok the deployment finally took.

clipped_quads <- ggplot(iucn_coral_fixed %>%
                      filter(!iucn_sid %in% (iucn_coral_fixed %>% 
                                               filter(perc > 100) %>% 
                                               .$iucn_sid)),
                    aes(x = ratio, y = perc, group = iucn_sid)) +
  geom_line(color = 'grey50', alpha = .5) +
  geom_point(aes(color = method)) +
  labs(x = 'Area ratio (smaller/larger)',
       y = 'Distribtion (%smaller in larger)',
       title = 'Coral species alignment, IUCN full range vs depth-clipped')

>>>>

clipped_quads <- ggplot(iucn_coral_fixed %>%
                      filter(!iucn_sid %in% (iucn_coral_fixed %>% 
                                               filter(perc > 100) %>% 
                                               .$iucn_sid)),
                    aes(x = ratio, y = perc, group = iucn_sid)) +
  geom_line(color = 'grey50', size = .5, alpha = .3) +
  geom_point(aes(color = method), size = 2) +
  labs(x = 'Area ratio (smaller/larger)',
       y = 'Distribtion (%smaller in larger)',
       title = 'Coral species alignment, IUCN full range vs depth-clipped')
